Robust Decorrelation of Errors in Quantum Gates by Random Gate Synthesis

### 2018-11-15 decorrelation/decorrelation.tex
adding notebook, and udpating paper with a short paragraph about 2q results

Another way of performing randomized deocupling is through mixing unitaries. In \cite{Campbell2017}, Campbell presents an algorithm that, given an oracle for generating unitaries close to a target, produces controls that are quadratically better in diamond norm than any of the individual controls generated by the oracle. In Campbell's work, he discusses such an oracle could be implemented via unitary synthesis approximations algorithms\cite{1612.01011}, and considers estimating and reducing resources costs that might arise during circuit compilation. In this paper we will we explore a different but related problem: synthesizing physical controls and making them robust to drift. Using optimal control routines as our oracle , we propose to inject additional decorrelating randomness into the system during physical gate synthesis through the use of \emph{robustly balanced controls} (RBCs).

@@

\subsection{2Q Gates}\label{2Q Gates}
 For a two-qubit example, we chose $ZZ(\frac{\pi}{2})=\exp{(-i\frac{\pi}{4}\sigma_z\otimes\sigma_z)}$. Our control Hamiltonian is given as:
\begin{equation} \label{eq:2Qham}
\begin{split}
H(\vec{\epsilon}, \vec{\delta}, \eta, t) = &\sum_{j=1}^2(\epsilon_j\sigma_z^j + (1 + \delta_j)(c_x^jx(t)\sigma_x^j + c_y^j(t)\sigma_y^j)) \\
&+ (1+\eta)c(t) \exp{(-i\frac{\pi}{4}\sigma_z^1\otimes\sigma_z^2})
\end{split}
\end{equation}
We again consider $\epsilon_j, \delta_j, \eta \sim .001$, a threshold infidelity of $1E-3$, and a Gaussian quadrature degree of $d=FILL IN$, however we increased the total evolution time to $T=FILL IN$, and increased the number of steps to $N=FILL IN$ so that the size of each time step was the same as in the one qubit example and so that the total evolution time was greater to allow GRAPE more opportunities to find non-trivial pulseshapes. The results also show a reduction of an order of magnitude in diamond norm about the origin, and for a wide neighborhood around it.

>>>>

Another way of performing randomized deocupling is through mixing unitaries. In \cite{Campbell2017}, Campbell presents an algorithm that, given an oracle for generating unitaries close to a target, produces controls that are quadratically better in diamond norm than any of the individual controls generated by the oracle. In Campbell's work, he discusses such an oracle could be implemented via unitary synthesis approximations algorithms\cite{1612.01011}, and considers estimating and reducing resources costs that might arise during circuit compilation. In this paper we will we explore a different but related problem: synthesizing physical controls and making them robust to drift. Using optimal control routines as our oracle, we propose to inject additional decorrelating randomness into the system during physical gate synthesis through the use of \emph{robustly balanced controls} (RBCs).

@@

\subsection{2Q Gates}\label{2Q Gates}
 For a two-qubit example, we chose $iSWAP$. Our control Hamiltonian is given as:
\begin{equation} \label{eq:2Qham}
\begin{split}
H(\vec{\epsilon}, \vec{\delta}, \eta, t) = &\sum_{j=1}^2(\epsilon_j\sigma_z^j + (1 + \delta_j)(c_x^jx(t)\sigma_x^j + c_y^j(t)\sigma_y^j)) \\
&+ k(XX + YY)
\end{split}
\end{equation}
We again consider $\epsilon_j, \delta_j \sim .001$, a threshold infidelity of $1E-3$, and a Gaussian quadrature degree of $d=FILL IN$. In the two qubit case, however, the evolution time was constrained by the interaction Hamiltonian. In particular, we required a time of FILLIN so that GRAPE could find controls that performed a high fidelity iSWAP. Due to the na\"ivety of GRAPE, however, all the controls generated have nearly the same sensitivity to $\epsilon_j$. If we want to generate an $\ell RBC$ for $\ell > 0$, we need to ensure that the derivatives of the controls produced by our routine are both small and various enough that they can be combined in a way that averages to zero. To this end, we manually produced a collection of so-called bang-bang decoupling sequences. An example of such a sequence is show in FILL IN A FIGURE HERE. These controls all are constructed in such a way that one of the two qubits is flipped for some duration of the gate, during which a fraction of accrued RZ errors from frequency detuning errors on either qubit can be echoed away. When the convex solver is given these controls, it finds an optimal weighting that performs comparably with the one qubit example.
